---
title: CV
name: Elizabeth
surname: Hare
position: "Quantitative Geneticist/Owner"
address: "Dog Genetics LLC, Astoria, NY"
phone: (718) 530-5575
pronouns: she/her
email: "lizhare@gmail.com"
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Liz Hare provides statistical, genetic, and genomic research services, as well as analyses for selective breeding. Her focus is on integrating research into the operations of working dog programs."  
output:
    vitae::markdowncv:
        theme: davewhipp
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```


## Employment

### Quantitative Geneticist/Owner, Dog Genetics LLC

* PennVet Working Dog Center (2014-2023)

    - Detector Dog Phenotype-Genotype Project  
	
        + Developed anew C-BARQ-based questionnaire for selection and study of detector dogs  
	    + Cleaned and Analyzed data from behavior tests and questionnaires  
	    + Produced organized, documented data sets for collaborators  
    	+ Wrote and maintained R code for analyses and internal reports with version control and emphasis on reusability  
	
    - Long-Term Behavior and Health Surveillance of Search-and_Rescue Dogs Responding to the 9/11 Attacks  
	
        + Planned project and obtained funding from the AKC Canine Health Foundation  
        + Analyzed survival data comparing search-and-rescue dogs who responded to 9/11 with dogs who were not deployed  
		+ Compared cause of death between deployed and non-deployed dogs  
		+ Fitted generalized additive models to compare how C-BARQ measures differed between deployed and non-deployed dogs  
	
	- Used statistical models to compare C-BARQ traits in dog populations  
	
	    + Search-and-rescue and pet dogs  
		+ Explosive detection and service dogs in a prison puppy program  
	
	- Calculated estimated breeding values (EBV) for selective breeding and advised on acceptance of donated dogs
	
* Leader Dogs for the Blind (2013-2015)  

    - Cleaned and organized pedigree, behavior, and health data  
	- Estinated heritabilities of key traits to assess possible results of selection
	- Calculated estimated breeding values and selection indices used to plan breedings
	- Taught breeding manager to clean and analyze data and use it to calculate EBVs; provided extensive and detailed written documentation  

* US Department of Homeland Security and TSA Canine Breeding and Development Center (2010-2013)
    - proposed and received funding for multi-year study of behavior and health genetics and genomics  
	- Supervised a Research Coordinator who built a database, entered behavior and health data, and collected and shipped DNA samples for genotyping  
	- Established heritability of work-related behaviors  
	- Provided EBVss to be used to select dogs with the highest genetic potential for important traits  
	- Used genotype data to look for genomic regions associated with key behaviors
	- Collaborated in an analysis to find genomic regions associated with successful completion of training


### Previous Positions Held

* Postdoctoral Associate/Research Associate Professor, South Texas Psychiatric Genetics Research Center, San Antonio, TX (2006-2010)  

    - Organized and cleaned data from multi-site international studies including pedigrees, diagnoses, and measured behavioral phenotypes  
    - Estimated heritabilities of the age of onset of schizophrenia and personality traits in families affected by bipolar disorder  
    - Provided statistical analyses for studies of genetic linkage and association and behavioral phenotypes (anxiety, substance use)
	
* Animal Improvement Programs Laboratory, USDA, Beltsville, MD (2002-2004)  

    - Analyzed rates of participation in dairy phenotype testing  
	- Characterized the US dairy cattle population by describing trends in length of herd testing participation and calving intervals  
	
* Research Associate, Animal Breeding and Genetics Group, Cornell University, Ithaca, NY (1998-2002)  

   - Designed and taught distance education courses in canine and feline genetics
   - Provided statistical analysis for studies on heritability of catalase levels in rams and and effects of day length on hormone concentration in rabbits  

```{r}
exampleDataFrame <-
  tribble(
    ~Year, ~Position, ~Institution, ~Where, ~Details,
    "1998-2002", "Research Associate", "Animal Breeding and Genetics Group, Cornell University", "Ithaca, NY", c("Designed and taught distance education courses in canine and feline genetics", "Provided statistical analysis for studies on heritability of catalase levels in rams and and effects of day length on hormone concentration in rabbits"))

# resource: https://pkg.mitchelloharawild.com/vitae/reference/cv_entries.html
exampleDataFrame %>%
  detailed_entries(
    where = Position, # first entry, in bold
    what = Institution, # second entry, in regular text
    when = Year, # year placed in the margin
    with = Where, # last entry, in parentheses
    why = Details # list of items
  )
```


## Volunteer Positions

```{r}

tribble(
  ~Year, ~Position, ~Org,
  "2022-2023", "Director of Data Management and Open Science", "ManyDogs Project",
  "2022-2023", "BookDash Contributor", "The Turing Way",
  "2019-2023", "Conference and Accessibility Teams", "FORWARDS Taskforce for Women and Other Underrepresented Minorities",
  "2010-2020", "Conference Organizer, Grant Writer", "PennVet Working Dog Center"
) %>%
    brief_entries(
    #glue::glue("{Position} at {Org}"),
    what = Position,
    when = Year,
    with = Org
  )
```

## Education

```{r}

tribble(
  ~Degree, ~Year, ~Institution, ~Where,
  "Ph.D., Genetics", 1998, "George Washington University", "Washington, DC",
  "BA, Biology", 1991, "Bryn Mawr College", "Bryn Mawr, PA"
  )  %>%
  detailed_entries(
    where = Degree, 
    what = Institution,
    when = Year, 
    with = Where
    )
  
```

## Selected Publications

```{r}
library(dplyr)
## knitr::write_bib(c("vitae", "tibble"), "citations02.bib")

bibliography_entries("citations02.bib") ##%>%
##  arrange(desc(author$family), issued)

```
 
